---
title: "Summary analyasis for H2O2-induced Loss of Heterozygocity"
author: "H Qin and E Guven"
date: "Spring, 2016"
output: html_document
---

```{r}
rm( list = ls() );
setwd("~/github/LOH_H2O2_2016/public/analysis")
```

# Load data from two previous studies. 

(1) Qin, Lu, and Goldfarb, 2008,
Genomic Instability Is Associated with Natural Life Span Variation in Saccharomyces cerevisiae
PLoS One. 2008 Jul 16;3(7):e2670. doi: 10.1371/journal.pone.0002670.
http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0002670

(2) Lu and Qin, 2006, 
Natural variation in replicative and chronological life spans of Saccharomyces cerevisiae.
Exp Gerontol. 2006 Apr;41(4):448-56.
http://www.ncbi.nlm.nih.gov/pubmed/16516427

```{r}
 list.files( path="data")
 tb = read.table("data/021307.summary.by.strain.csv", header=T, sep="\t");
 tb.old = tb;
 labels = names( tb.old );
 tb = tb.old[, c("strain","ARLS","R0","G","CLS","Tc", "Tg","Tmmax","Tbmax", "Td", "Tdmax","TLmax","Lmax", 
 "b.max", "b.min", "strains", "L0.all", "L0.small" , "Pbt0","Pb0.5t0", "Pbt0.b") ];
 tb$CLS.vs.Tc = tb$CLS / tb$Tc; 
 tb$Tg.vs.Tc = tb$Tg / tb$Tc;
 tb$strain = as.character(tb$strain)
 tb.old = tb;
 tb = tb.old[1:13,] #remove rad52DD
 tb.test = tb[1:11,]   
```

```{r}
 summary(lm(Tg.vs.Tc ~ ARLS, data=tb.test)) #re-run the old results, just to double-check
 summary(lm( 1/Tg.vs.Tc ~ ARLS, data=tb.test)) # negative, p=0.012 R2=0.52
 plot( tb.test$Tg.vs.Tc ~ tb.test$ARLS, col='red', pch=19, xlab='ARLS', ylab='Tg/Tc' )
 text(tb.test$ARLS, tb.test$Tg.vs.Tc, tb.test$strains)
```

# Load data for H2O2-induced LOH 
```{r}
 tb2 = read.csv("data/LOHH2O2_dataset.csv") 
```

Merge tb and tb2. The merged table is 'tb3' 
```{r}
 tb2$strain = tb2$strains
 tb3 = merge(tb, tb2, by='strain')
 tb3 = tb3[ , -(grep('strains', names(tb3))) ]
```

# Generate Figure 3A, plot of Cb/Cv ~ ARLS. 

```{r}
 summary(lm(tb3$Cb.vs.Cv ~ tb3$ARLS)) #p 0.039
 plot( tb3$Cb.vs.Cv ~ tb3$ARLS, col='blue', pch=19, xlab='Average Replicative Lifespan', ylab='sensitive<= Cb/Cv => tolerant', xlim=c(22,38),ylim=c(-0.1,2.8), main="Tolerance to H2O2 induced LOH, Cb/Cv ~ average RLS")
 text(tb3$ARLS + 0.5, tb3$Cb.vs.Cv+0.1, tb3$strain)
 m = lm(tb3$Cb.vs.Cv ~ tb3$ARLS )
 abline(m, col='red', lty=2, lwd=2)
 text(26, 2.0, "p=0.039, R2=0.36")
```


# Figure 3B. Plot of Cb/Cv to mitotic asymmetry measure L0 

```{r}
 par(font=2)
 summary(lm( tb3$Cb.vs.Cv ~  tb3$L0.all)) # p=0.0079
 plot( tb3$Cb.vs.Cv ~ tb3$L0.all, col='blue', pch=19, xlab='Better asymmetry <- L0 -> Worse asymmetry', ylab='sensitive <- Cb/Cv ->tolerant', xlim=c(0, 0.3),ylim=c(-0.1,2.5), main="Cb/Cv ~ an inverse measure of mitotic asymmetry L0")
 text(tb3$L0.all + 0.01, tb3$Cb.vs.Cv+0.1, tb3$strain)
 m = lm(tb3$Cb.vs.Cv ~ tb3$L0.all )
 abline(m, col='red', lty=2, lwd=2)
 text(0.1, 2.0, "p=0.0079 R2=0.56")
```

### Try 1/L0 to verify the above result.  
```{r}
 tb3$One.vs.L0.all = 1 / tb3$L0.all  #use 1/L0 maybe confusing when people try to compare this study with Qin08 results.
 summary(lm( tb3$Cb.vs.Cv ~  tb3$One.vs.L0.all)) # p=0.039
 plot( tb3$Cb.vs.Cv ~ tb3$One.vs.L0.all, col='blue', pch=19, xlab=' 1/L0', ylab='Cb/Cv', xlim=c(2,19),ylim=c(0.2, 2.8) )
 text(tb3$One.vs.L0.all + 0.01, tb3$Cb.vs.Cv+0.1, tb3$strain)
 m = lm(tb3$Cb.vs.Cv ~ tb3$One.vs.L0.all )
 abline(m, col='red', lty=2, lwd=2)
```

 
# Figure 4B. Side-by-side bar-plots of Tg/Tc and Cb/Cv

```{r}
 mystep=0.2
 my.breaks = seq( 0.2,  round(max( c( tb3$Cb.vs.Cv, tb3$Tg.vs.Tc )) + 0.2, 1) ,by= mystep ); 
 h.H2O2  <- hist( tb3$Cb.vs.Cv, br= my.breaks, xlab = "Cb/Cv", ylab = "relative density", freq=F, plot=F ) ; 
 h.aging <- hist(tb$Tg.vs.Tc, br= my.breaks, xlab = "Tg/Tc",  ylab = "relative density", freq=F, plot=F ) ;
 
 #generate the comparison table
 bins <-  data.frame( rbind(h.H2O2$density,h.aging$density) )  ;
 my.mids = my.breaks[-length(my.breaks)] + mystep/2
 names( bins ) <- my.mids
 row.names(bins) <- c( "H2O2", "Chronological Aging" )
 bins

 barplot( as.matrix(bins), beside=T, col=c("black","gray"), ylab="Relative Frequency", xlab="Ratios", legend= c( "Cb/Cv H2O2", "Tg/Tc CLS" )  );
 title(main="Contrasting LOH onsets in CLS and H2O2 treatment" )

 ks.test(tb3$Cb.vs.Cv, tb3$Tg.vs.Tc) #p=0.031
```


# Figure 4D. Plot of $(\frac{Tg}{Tc} / \frac{Cb}{Cv})$  ~ L0


```{r}
tb3$TgTc.vs.CbCv =  tb3$Tg.vs.Tc / tb3$Cb.vs.Cv 

summary(lm(tb3$L0.all ~  tb3$TgTc.vs.CbCv ))
m = lm(tb3$L0.all ~  tb3$TgTc.vs.CbCv)
par(font=2) 
plot( tb3$L0.all ~ tb3$TgTc.vs.CbCv, pch=19, col="red", 
      ylab = "Better asymmetry <- L0 -> Worse assymetry",
      xlab = "Weaker suppression <- (Tg/Tc)/(Cb/Cv) -> Stronger suppression",
      main="Mitotic asymmetry ~ Ability to suppress endogenous oxidative stress",
      xlim = c(-0.05, 4.5), ylim=c(0, 0.3))
abline(m, col="blue")
text( tb3$TgTc.vs.CbCv, tb3$L0.all+0.015, tb3$strain)
text( 3, 0.28, "p=0.004,R2=0.62")
```


